%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mosabcv}

% For mathematical symbols
\usepackage{amsmath}

\usepackage[colorlinks = true,
linkcolor = black,
urlcolor = black,
citecolor = black,
anchorcolor = black]{hyperref}

% Set applicant's personal data for header
\name{Mosab A. Ibrahim}
\address{London \linebreak United Kingdom}
\contacts{+44 741 565 4481 \linebreak mosab.a.ibrahim@gmail.com}

\begin{document}

% Print the header
\makeheader{}

% Print the content
%%%%%%%%%%%%%%%%%%% Employment
\begin{cvsection}{Employment}
  \begin{cvsubsection}{Site Reliability
    Engineer}{\href{https://gocardless.com}{GoCardless}}{March 2019 ---
    Present}
    \begin{itemize}
      \item Protect, provide for, and progress the software and systems that
        make up the GoCardless product, supporting product teams in the
        deployment of high quality services.
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{Software Engineer}{WeQ Global Tech GmbH}{November 2017 ---
    March 2019}    \begin{itemize}
      \item Developed, deployed, \& maintained customer facing microservices
        (Java/PHP) handling over a billion requests/day.
      \item Created, and maintained infrastructure as code for new and legacy
        systems/microservices.
      \item Owned services uptime, performed systems troubleshooting \&
        debugging and participated in on-call rotations.
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{Sr. Software \& Platform Engineer}{zlabs
    (zlien.com)}{March 2013 --- October 2017}
    \begin{itemize}
      \item Lead a team designing \& developing an internal platform for data
        verification and research process.
      \item Migrated the zlien.com platform to a microservices based
        architecture.
      \item Designed \& building zlien API that ingests 100K+ transactions
        every week from our customers' systems.
      \item Reduced release time from an average of 1--2 days, to an average of
        3--7 minutes by automating the process.
      \item Turned the few downtimes a week into 99.9\% uptime of the platform
        for the past 4 years.
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{Software Engineer}{Inmobly}{January 2012 --- May 2012}
    \begin{itemize}
      \item Designed, developed \& deployed Python backends for two mobile apps
        that recorded and streamed videos.
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{Lead Software Engineer}{Wuzzuf.net}{April 2010 --- April
    2011}
    \begin{itemize}
      \item Designed, and lead the team to implement the software and
        infrastructure architecture that handles 5 million CVs and 1M+ of job
        postings.
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{Software Engineer}{Citex Software}{April 2010 --- April
    2011}
    \begin{itemize}
      \item Reverse engineered on-premise industrial printing system workflow \&
        developed an online drupal system to integrate with it in order to
        provide online ordering features to customers.
      \item Developed a PHP template engine reducing the amount of templating
        development work to 20\%.
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{PHP Developer}{Media International}{January 2007 ---
    September 2008}
    \begin{itemize}
      \item Designed, developed, deployed and maintained PHP projects (linux
        servers, load balancers, MySQL).
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{PHP Developer}{20at.com}{January 2004 --- December 2006}
    A rebellious first of a kind editorial platform by youth in the middle east
    \begin{itemize}
      \item Rebuilt the portal migrating from a legacy system, and built new
        sites and platforms.
    \end{itemize}
  \end{cvsubsection}

\end{cvsection}

%%%%%%%%%%%%%%%%%%% Education
\begin{cvsection}{Education}
  \begin{cvsubsection}{Cairo, Egypt}{University of Cairo}{Fall 2003 --- Summer 2007}
    \begin{itemize}
      \item Moved between computer \& civil engineering, architecture,
        and commerce, before dropping out for family reasons.
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}

%%%%%%%%%%%%%%%%%%% Open Source Projects
\begin{cvsection}{Open Source Projects}
  \begin{cvsubsection}{}{}{}
    \begin{itemize}
      \item \textbf{\href{https://github.com/mos3abof/toggl_target}{Toggl
        Target}} (2013). CLI working hours planning tool. Featured in Toggl API
        documentation. Python, Requests.
      \item \textbf{\href{https://www.gridstatusnow.com}{Grid Status Now}}
        (2014). Egypt's power grid load status as an open source web service.
        PHP, Symfony.
      \item \textbf{\href{https://power-close.com/}{Power Close}} (2014). A
        browser addon to close tabs based on domain or keyword. JavaScript,
        Firefox, Chrome.
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}

%%%%%%%%%%%%%%%%%%% Languages and Technologies
\begin{cvsection}{Programming Languages \& Technologies}
  \begin{cvsubsection}{}{}{}
    \begin{itemize}
      \item Python; PHP;\ Go; Bash; SQL;\ JavaScript; Java; C;\  Ruby;
        Linux System Programming;
      \item Linux; Linux Internals; TCP/IP;\ Apache; MySQL;\ Git; Mercurial;
        Docker; Docker Swarm; Ansible; Amazon AWS;\ Google Cloud; Kubernetes;
        PostgreSQL;\ Terraform; Redis; Kafka; Chef; Prometheus; Grafana;
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}

%%%%%%%%%%%%%%%%%%% Additional links
\begin{cvsection}{Additional Links \& Info}
  \begin{cvsubsection}{}{}{}
    \begin{itemize}
      \item \textbf{Personal Website:}
        \href{https://mosab.co.uk}{https://mosab.co.uk}
      \item \textbf{Github Profile:}
        \href{https://github.com/mos3abof}{https://github.com/mos3abof}
      \item \textbf{Linkedin Profile:}
        \href{https://www.linkedin.com/in/mosab}{https://www.linkedin.com/in/mosab}
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}
\end{document}
