%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\textbf{Production Engineer}} % Job title
    {Meta / Formerly Facebook} % Organisation
    {London, United Kingdom} % Location
    {Mar 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Production Engineering combines software, systems, and infra engineering. Production Engineers
      are known for their ability to work on a wide variety of projects across multiple teams.
      Whether writing code or debugging hard problems in production, our team makes sure that Meta
      apps and services are reliable and scalable. Production Engineers help the over 3.6 billion
      monthly users around the world who depend on Meta products like Instagram, WhatsApp, Oculus
      and Videos as well as backend services like Storage, Cache and Network.}
      \item {\textbf{Technical Skills:} Python, Rust, Linux, MySQL, ZippyDB, Mercurial, Distributed Systems}
      \end{cvitems}
    }

  \cventry
    {\textbf{Senior Site Reliability Engineer}} % Job title
    {Twitter} % Organisation
    {London, United Kingdom} % Location
    {May 2020 - Mar 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Improved the availability, scalability, performance and reliability of Twitter’s production services.}
      \item {Worked as part of the SRE team providing Twitter teams with Databases infrastructure(MySQL, PostgreSQL, Vertica, Druid).}
      \item {Designed and built a service that automates and massively reduces toil, providing a
          98\% drop in the time to provision resources, which works out to >100k saving in person
          hours (>139 person months, >11.5 person years) in the next few years.}
      \item {\textbf{Technical Skills:} Python, Flask, SQLAlchemy, Linux, MySQL, PostgreSQL, Vertica, Druid, Git}
      \end{cvitems}
    }

  \cventry
    {\textbf{Site Reliability Engineer}} % Job title
    {GoCardless} % Organisation
    {London, United Kingdom} % Location
    {Mar 2019 - Mar 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Protect, provide for, and progress the software and systems that make up the GoCardless product, supporting product teams in the deployment of high quality services.}
      \item {\textbf{Technical Skills:} Golang, PostgreSQL, GCP, Kubernetes, Terraform, Helm,
        Elastic Search, Kibana, Linuxa, Docker, Git, Prometheus, Grafana, Thanos}
      \end{cvitems}
    }

  \cventry
    {\textbf{Software Engineer}} % Job title
    {WeQ Global Tech GmbH} % Organisation
    {Berlin - Germany} % Location
    {Nov 2017 - Mar 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed, deployed \&maintained customer facing microservices handling over a billion requests/day.}
        \item {Created and maintained infrastructure as code for new and legacy systems/microservices.}
        \item {\textbf{Technical Skills:} PHP, Java, Spring Boot, Kafka, AWS, Docker, Doscker Swarm,
          Terraform, Jenkins, MySQL, MongoDB, Prometheus, Grafana}
      \end{cvitems}
    }

  \cventry
    {\textbf{Sr. Software \& Platform Engineer}} % Job title
    {Levelset (formerly zlabs)} % Organisation
    {Cairo - Egypt} % Location
    {Mar 2013 - Oct 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead a team designing \& developing an internal platform for data verification and research process.}
        \item {Migrated the levelset.com platform to a microservices based architecture.}
        \item {Designed \& built the API that ingests 100K+ transactions every week from enterprise customers’ systems.}
        \item {Optimised time to release by orders of magnitudes (2 days to 5 minutes), and improved
          uptime (99.9\% from several outages a week).}
        \item {\textbf{Technical Skills:} PHP, Symfony, Linux, AWS, RabbitMQ, Soap API, Rest API,
          Jenkins, MySQL, Git, Nagios, New Relic}
      \end{cvitems}
    }

  \cventry
    {\textbf{Senior Software Engineer}} % Job title
    {Handmade Studios} % Organisation
    {Cairo - Egypt} % Location
    {Jun 2012 - Feb 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed \& maintained an editorial website for entrepreneurs ands tartups.}
        \item {\textbf{Technical Skills:} PHP, Symfony, Linux, AWS, Git}
      \end{cvitems}
    }


  \cventry
    {\textbf{Senior Software Engineer}} % Job title
    {Inmobly} % Organisation
    {Cairo - Egypt} % Location
    {Nov 2011 - May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed \& deployed API backends for two mobile apps that recorded ands treamed videos.}
        \item {\textbf{Technical Skills:} Python, Flask, SQLAlchemy, Rest, AWS, SVN}
      \end{cvitems}
    }

  \cventry
    {\textbf{Technical Consultant}} % Job title
    {Bluw i LTD} % Organisation
    {Cairo - Egypt} % Location
    {Jun 2011 - Sep 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a social network for entrepreneurs to raise funds from angel investors.}
        \item {\textbf{Technical Skills:} PHP, Drupal, AWS, Git}
      \end{cvitems}
    }

  \cventry
    {\textbf{Lead Software Engineer}} % Job title
    {Wuzzuf.net} % Organisation
    {Cairo - Egypt} % Location
    {Apr 2010 - Apr 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed the architecture for Wuzzuf.net}
      \item {Lead the team in implementin wuzzuf.net (Egypt’s leading hiring platform).}
        \item {Collaborated closely with the company’s CTO.}
        \item {Designed, created, monitored and maintained the infrastructure of wuzzuf.net.}
        \item {\textbf{Technical Skills:} PHP, CakePHP, Doctrine ORM, AWS, MySQL Mercurial}
      \end{cvitems}
    }

  \cventry
    {\textbf{Senior Software Engineer}} % Job title
    {Arabia Inform} % Organisation
    {Cairo - Egypt} % Location
    {Nov 2009 - Apr 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built an archiving solution for media with an advanced search index and media encoding features.}
        \item {Implemented and deployed an ads management solution for the company’s websites network.}
        \item {Collaborated with other teams on infra upgrade projects and migrations.}
        \item {\textbf{Technical Skills:} PHP, Drupal, OpenX, AWS, Git}
      \end{cvitems}
    }

  \cventry
    {\textbf{Software Engineer}} % Job title
    {Citex Software} % Organisation
    {Cairo - Egypt} % Location
    {Oct 2008 - Nov 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a social network for entrepreneurs to raise funds from angel investors.}
        \item {\textbf{Technical Skills:} PHP, Drupal, AWS, Git, Nagios}
      \end{cvitems}
    }

  \cventry
    {\textbf{PHP Developer}} % Job title
    {Media International} % Organisation
    {Cairo - Egypt} % Location
    {Jan 2007 - Sep 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed, deployed and maintained various PHP projects for customer.}
        \item {Designed and executed data migration projects for some of our clients from legacy systems to solutions developed by our team.}
        \item {Surveyed andr eviewed tools for internal use by our team.}
        \item {Installed and configured load balancing linux web servers and implemented MySQL replication and file synchronization solutions.}
        \item {Monitored the servers, resolved production issues, and maintained service uptime.}
        \item {\textbf{Technical Skills:} PHP, Drupal, Joomla, Moodle, Linux, MySQL, Nagios}
      \end{cvitems}
    }

  \cventry
    {\textbf{PHP Developer}} % Job title
    {20at.com} % Organisation
    {Cairo - Egypt} % Location
    {Jun 2004 - Dec 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a new content management solution (CMS) from scratch to meet the editorial and business requirements}
        \item {Designed and executed data migration plan from the legacy version of thewebsite to the newly developed system.}
        \item {Maintained the online website codebase and applied bug and security fixes.}
        \item {Developed new features and sub-portals in reaction to business needs and special current events (e.g. world cup
2006).}
        \item {\textbf{Technical Skills:} PHP, Linux, MySQL, Dedicated Linux Hosting, S/FTP}
      \end{cvitems}
    }
\end{cventries}
